---
title: "Random Number Generator"
author: "Abul Kayash"
date: "16 September 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(raster)
library(rgdal)
library(jpeg)
library (imager)
```

## Random Number Gerator Functionality

This Shiny app generates  random draws from normal distribuitions and plots the values on a histogram.
 
## Access and Source Code

- The app is hosted at:
    https://abulkayash.shinyapps.io/randomng/
    
    
- The source code and supporting documentation may be found in the follwoing GitHub site:
  https://github.com/AbulKayash/randomNG



## Input Parameters

There are three input parameters

- Sample Size
    - The number of normally  distributed values generated
- bins
    - Number of bins bins used in the histogram
- sd
    - Standard deviation of the normal ditribution




## The Shiny App GUI




```{r interface}

image <- load.image("ShinyApp.png")
plot(image, axes=FALSE)

```

